The limits of self commitment and private paternalism \thanks{}

### 2022-12-20 OA.tex
revision of text by enrique, frank and isaac

\section{ Further results}
\vspace{.2in}

\subsection{Some materials}

@@

\subsection{Pictures}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
    \end{subfigure}
    \begin{subfigure}{0.42\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
    \end{subfigure}

    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

@@

%\begin{figure}[H]
%        \caption{Booklet with product information}
%    \label{micas}
%    \begin{center}
%        \centering
%        \includegraphics[width=\textwidth]{micas.pdf}
%    \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ }
%\end{figure}

%\begin{figure}[H]
%     \caption{Booklet with product information translated}
%    \label{booklet_translate2}
%    \begin{center}
%    \begin{subfigure}{.9\textwidth}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
%    \end{subfigure}
    %\begin{subfigure}{0.55\textwidth}
    %   \centering
    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
    %\end{subfigure}
%    \end{center}
%\end{figure}

@@

%\begin{table}[H]
%\caption{Survey's non-response balance}
%\label{balance_response}
%\begin{center}
%\scriptsize{\input{./Tables/balance_response.tex}}
%\end{center}
% \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not. We use this as an assessment of external validity. Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments. Panel A studies the baseline survey, while Panel B focuses on the exit survey. The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
%\textit{Do file: } \texttt{balance\_response.do}
%\end{table}

@@

\begin{comment}
\begin{table}[H]
\caption{Reincidence SS}
\label{tab_reincidence}
\begin{center}
\scriptsize{\input{./Tables/tab_reincidence.tex}}
\end{center}
 \scriptsize
%\textit{Do file: } \texttt{tab\_reincidence.do}
\end{table}

\begin{table}[H]
\caption{Summary statistics (exit survey)}
\label{SS_exit}
\begin{center}
\scriptsize{\input{./Tables/SS_exit.tex}}
\end{center}
 \scriptsize We carried out an exit survey. It had a small response rate and we don't use it in the paper. Here it shows that the characteristics of those that responded it are balanced across arms (Panel B). Panel A reports outcomes.
%\textit{Do file: } \texttt{ss.do}
\end{table}
\end{comment}

@@

\begin{table}[H]
\caption{Effects on several definitions of cost - Soft arms}
\label{table_robustness_fc_soft}
\begin{center}
\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
\end{table}

@@

\begin{table}[H]
\caption{Intermediate outcomes - Soft arms}
\label{mechanisms_soft}
\begin{center}
\scriptsize{\input{./Tables/mechanism_soft.tex}}
\end{center}

%\textit{Do file: } \texttt{mechanisms\_soft.do}
\end{table}

@@

@@

% \begin{figure}[H]
%         \caption{FC restricted to 115 days}
%     \label{fc_pro_2_115}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
%     \end{center}
%      \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
%      %\textit{Do file: }  \texttt{fc\_te\_115.do}
% \end{figure}

% \begin{figure}[H]
%         \caption{Financial cost effect: charging all fees}
%     \label{fc_allfee}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
%     \end{center}
%     \scriptsize
%      This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees. This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract. The circles indicate the quantile treatment effects, while the cross is the (OLS) mean. We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
%      %\texttt{fc\_all\_fee.do}
% \end{figure}

% \begin{figure}[H]
%         \caption{FC as \% of loan - treatment effect}
%     \label{fc_perc}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
%     \end{center}
%      \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
%      %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
% \end{figure}

\begin{figure}[H]
    \caption{Relationship between treatment effects}
    \label{induced_to_pay_early}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
    \end{subfigure}
    \end{center}
       \scriptsize 
       This figure plots relationships between \textit{treatment effects}. Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made. The treatments effects were calculated using \cite{atheygrf}. In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost. In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn. Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control). Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
      %\textit{Do file: }  \texttt{binscatter\_hte.do}
\end{figure}

% \begin{figure}[H]
%         \caption{Repeat purchase before 30/60 days}
%     \label{reincidence_before}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
%     \end{center}
%      \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
%      %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
% \end{figure}

\vspace{.3in}

\subsection{FOSD: fee forcing vs status quo financial cost distributions}

@@

\newpage
\subsection{Causal Random Forest and HTE}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
%     \label{HTE_fee_forcing}
%     \begin{center}
%     %\begin{subfigure}{0.4\textwidth}
%     %    \caption{Financial cost}
%     %    \centering
%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
%     %\end{subfigure}
%     \begin{subfigure}{0.7\textwidth}
%         \caption{Determinants of effects}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
%     \end{subfigure}

%     %\begin{subfigure}{0.4\textwidth}
%     %    \caption{Losing Pawn}
%     %    \centering
%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
%     %\end{subfigure}
%     %\begin{subfigure}{0.4\textwidth}
%     %    \caption*{}
%     %    \centering
%     %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
%     %\end{subfigure}
%     \end{center}
%      \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$. The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc. See this Appendix for a transcription of the survey).
%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
%     \label{heterogeneous_te_3}
%     \begin{center}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Financial cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
%     \end{subfigure}

%     \begin{subfigure}{0.4\textwidth}
%         \caption{Losing Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
%     \end{subfigure}
%     \end{center}
%      \scriptsize
%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect - Choice/Fee}
%     \label{heterogeneous_te_4}
%     \begin{center}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Financial cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
%     \end{subfigure}

%     \begin{subfigure}{0.4\textwidth}
%         \caption{Losing Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
%     \end{subfigure}
%     \end{center}
%      \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect - Choice/Promise}
%     \label{heterogeneous_te_5}
%     \begin{center}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Financial cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Losing Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
%     \end{subfigure}
%     \end{center}
%      \footnotesize \textit{Notes: } 
%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

%\begin{figure}[H]
%    \caption{Heterogeneous Treatment Effect (FC survey) - All arms}
%    \label{heterogeneous_te_fcsurvey_all}
%    \begin{center}
%    \begin{subfigure}{0.4\textwidth}
%        \caption{Forcing/Fee}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_2.pdf}
%    \end{subfigure}
%    \begin{subfigure}{0.4\textwidth}
%        \caption{Forcing/Promise}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_3.pdf}
%    \end{subfigure}

%    \begin{subfigure}{0.4\textwidth}
%        \caption{Choice/Fee}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_4.pdf}
%    \end{subfigure}
%    \begin{subfigure}{0.4\textwidth}
%        \caption{Choice/Promise}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_5.pdf}
%    \end{subfigure}
%    \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
%\end{figure}

@@

\subsubsection{Finite mixture model }\label{fmm_section}

We assume the following structural model : Each individual $i$ is of type  $k\in\{1, 2\}$ with probability $\alpha_{i,k}$. We assume it follows a logit distribution:
\begin{align*}
\label{dist_alpha}
    \alpha_{i,k} = \Pr(\text{Type}_i = k \;|\; \mathbf{W}_{i}) = \frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}
\end{align*}

where $\mathbf{W}_i$ are observable characteristics. This characteristics include choice for commitment, present bias, subjective probability of recovery, etc, which might be indicators of naivete vs sophistication.

Now, given their type, each individual makes a choice to default or not $c_{i,k} \in \{1,2\}$, based on other set of observable characteristics $\mathbf{X}_i$ (subjective \& objective value of the loan). We will assume there is a continuous latent variable $Y_{i,k,c}$ distributed as
\[Y_{i,k,c} = \beta_{c,k}\mathbf{X}_{i} +\epsilon_{c,k}\]
with\footnote{We can impose other errors, and even impose a covariance structure, for instance if $(\epsilon_{c,k})_{c}\sim\mathcal{N}(0,\Sigma_k)$, we arrive to the Multinomial Probit.} $\epsilon_{c;k}\sim\operatorname{EV}(0,1)$. This latent variable can be thought of as the utility associated with individual $i$, being type $k$, making choice $c$.

Thus, the density for each individual $i$ being type $k$ is
\[f(c_i,\mathbf{X}_i; \bm\beta_{k}) = \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=4]}\]

Finally, the generative model is then a mixture model with density given by,
\begin{align*}
    f(c_i ,\mathbf{W}_i, \mathbf{X}_i; \bm{\gamma},\bm{\beta}) &= \sum_{k=1}^K \alpha_k f(c_i,\mathbf{X}_i; \bm\beta_{k}) \\
    &= \sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
\end{align*}

where $\alpha\sim \operatorname{Categorical}$, and $\gamma_{K} = \beta_{4,k}=0$ for identification purposes.

Then the (incomplete) log-likelihood function is
\begin{align*}
    \ell(\bm{\gamma}, \bm{\beta}; c, \mathbf{W},  \mathbf{X}) = \sum_{i=1}^n \log\sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
\end{align*}

, thus we estimate parameters $(\bm{\gamma}, \bm{\beta})$ with an EM algorithm using choice (default), and observable characteristics: $(c_i,\mathbf{W}_i,\mathbf{X}_i)$.

\begin{table}[H]
\caption{FMM}
\label{fmm_table}
\begin{center}
\scriptsize{\input{./Tables/fmm_types.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fmm.do}
\end{table}

\begin{figure}[H]
    \caption{Treatment effect of Type 1 individuals}
    \label{fmm_hte}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}       
            \caption{Probability of Type 1 vs HTE}
            \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
    \end{subfigure}
   \begin{subfigure}{0.475\textwidth}
        \caption{Type 1 vs HTE}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize 
     After estimating the FMM, we compute the probability for each individual of belonging to each class, the x-axis represents the probability of being Type $1$, while the y-axis shows the HTE. A positive relation indicates that Type $1$ individuals are more benefited from commitment.
      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
\end{figure}

\subsubsection{LATE: ToT \& TuT}
\vspace{.2in}
\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

@@

\subsection{New results}

\begin{table}[H]
\caption{Effect of frequent payment in observational data}
\label{te_obs}
\begin{center}
\scriptsize{\input{./Tables/def_te_obs.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{def\_te\_obs.do}
\end{table}

% \begin{figure}[H]
%     \caption{Treatment effects pooling all arms}
%     \label{pooled_arms_te}
%     \begin{center}
%     \begin{subfigure}{0.45\textwidth}
%         \caption{Financial Cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.45\textwidth}
%         \caption{Lost Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
%     \end{subfigure}
%     \end{center}
%      \scriptsize
%       %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
% \end{figure}

% \begin{figure}[H]
%         \caption{Treatment effect decomposition of the Financial Cost }
%     \label{reg_int_pro_2}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
%     \end{center}
%      \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a). It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230). In the right axis we show the treatment effect on the payed fees. Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
%      %\textit{Do file: }  \texttt{reg_\int.do}
% \end{figure}

% \begin{figure}[H]
%         \caption{Frequency of renewals}
%     \label{ref_dist}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.60\textwidth]{Figuras/ref_dist.pdf}
%     \end{center}
%      \scriptsize  This Figure shows the occurrence and frequency of renewals. It locates in time, respective to the day the loan started, when the renewal occurs for both the first and second renewal. Note that the first renewal is concentrated around 100 days, while the second is concentrated around the 200 days, corresponding to the first and second cycle. 
%      %\textit{Do file: }  \texttt{ref_\dist.do}
% \end{figure}

%\begin{figure}[H]
%    \caption{Exit Survey: reasons to pawn or not again with monthly payments}
%    \label{reasons}
%    \begin{center}
%    \begin{subfigure}{0.5\textwidth}
%        \caption{Pawn again because:}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/razones_si.pdf}
%    \end{subfigure}
%    \begin{subfigure}{0.5\textwidth}
%        \caption{Not pawn because:}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/razones_no.pdf}
%    \end{subfigure}
%    \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ \textit{Do file: }  \texttt{ss.do}}
%\end{figure}

%\begin{figure}[H]
%    \caption{Decomposition of the mistakes by `Overconfidence' for Promise Arms}
%    \label{Promise_errors}
%    \begin{center}
%    \begin{subfigure}{0.6\textwidth}
%        \caption{Promise}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_promise.pdf}
%    \end{subfigure}
%    \end{center}
%     \footnotesize 
%     \textit{Notes: }  Decomposition of the percentage of mistakes by overconfidence. 
%       \textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_decomposition.do}
%\end{figure}

%\begin{figure}[H]
%        \caption{Types of agents that incur in different FC}
%    \label{components_fc}
%    \begin{center}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
%    \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
%\end{figure}

>>>>

\section{ }
\vspace{.2in}

@@

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
    \end{subfigure}
    \begin{subfigure}{0.42\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

@@

@@

@@

@@

\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
    \end{center}
     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
\end{figure}

@@

\begin{table}[H]
\caption{Multiple-loans robustness check}
\label{multiple_loans}
\begin{center}
\scriptsize{\input{./Tables/multiple_loans.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{multiple\_loans.do}
\end{table}

@@

\begin{figure}[H]
        \caption{Survival graph}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

\begin{figure}[H]
        \caption{\% of payment over time}
    \label{porc_payment_over_time}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
        \caption{Unconditional}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Conditional on default}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
\end{figure}

@@

@@

\subsection{Testing for heterogeneity}
Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have 
\[
\text{ATE}(X_i) \equiv \mathbbm{E}[\Delta_i |X_i] = \mathbbm{E}[\Delta_i] \equiv \text{ATE}
\]
for any covariates $X_i$ that vary across $i$. If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a ``training set'' and a \todo{80/20 split?}{``test set.''} In the first step, we apply random forests to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the average treatment effect function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.

In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.

\todo[inline]{Discuss the results here.}

\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy

\begin{table}[H]
\begin{center}
\scriptsize{\input{./Tables/test_calibration_2.tex}}
\end{center}
\end{table}

}

\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting? If we cluster standard errors at the branch-day level, we should take this into account when we split. (2) How are you carrying out inference for $\beta_2$? Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split. The latter is a bit more involved, since one accounts for uncertainty arising from different splits. (3) What are the details of the random forest procedure employed here? (Tuning parameters choice, etc.) We should put them into the appendix.}

@@

\subsection{LATE: ToT \& TuT}
\vspace{.2in}
\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

@@

\newpage 
\newpage
\subsection{Causal Random Forest and HTE}

\begin{figure}[H]
    \caption{Choice of contracts and treatment effects}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{Financial value of mistake}
        \centering
        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}

    \bigskip

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\% better when forced to forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}

    \end{subfigure}
    %     \begin{subfigure}{0.45\textwidth}
    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
    %     \centering
    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
    % \end{subfigure}

    \end{center}
        \scriptsize
        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract. To do this we proceed in two steps. First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm. We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests. Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s. Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan. $z$\% is a level of tolerance we can vary and we plot it in the X-axis. The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''. We use bootstrap to tighten the confidence intervals (CIs). \cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal. We compute the HTE ($\mu$) together with standard errors ($\sigma$) . For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) . This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI. Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident. Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract. To do this we proceed in two steps as well. First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$. We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice. 
        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.  Using all bins we estimate a slope of zero in the relationship. Using the 80 right most points, we estimate a \textit{positive} relationship.
        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
\end{figure}
